\vspace{-1in}
\chapter{Literature Survey}
A distributed solution is required, as it is not practical or cost efficient, in many cases, to maintain idle service/hardware provision merely to keep up with all identified demands. Indeed it is not possible, when dealing with such complexity, to fully detail all system future states; it is thus necessary to allow local reasoning, through distributed algorithms, on the current system state. Thus efficient load balancing cannot be achieved by individually assigning jobs to appropriate servers as the Cloud computing systems scale up and become more complex; rather jobs must inevitably be assigned with some uncertainty attached. This gives some immediate possible methods for load balancing in large scale Cloud systems, which are discussed here \cite {Ratan}. \\[0.2cm]
In biased random sampling, a nodes in-degree (node capacity) is mapped to its free resources. When a node receives a new job, it will remove one of its incoming edges to decrease its in-degree and indicate that its available resources are reduced. In the same way, when the node finishes a job, it will add an edge to itself to increase its in-degree. The process of adding and removing incoming edges is done by random sampling. Random sampling is the process whereby the nodes in the network are randomly picked up with equal probability. The sampling walk starts at some fixed node, and at each step, it moves to a neighbor node chosen randomly according to an arbitrary distribution. Then, the last node in the course of the sampling walk will be selected for the load assignment \cite {Randles1}.\\[0.2cm]
Honeybee Foraging is one of a number of applications inspired by the believed behavior of a colony of honeybees foraging and harvesting food. Forager bees are sent to search for suitable sources of food; when one is found, they return to the hive to advertise this using a display to the hive known as a “waggle dance”. The suitability of the food source may be derived from the quantity or quality of nectar the bee harvested, or its distance from the hive. This is communicated through the waggle dance display. Honey bees then follow the forager back to the discovered food source and begin to harvest it. This approach has been used for various applications in computing \cite {Randles1}.\\[0.2cm]
Experiments have been conducted to assess and analyze these procedures for load balancing claiming that none of the load balancing methods are mutually exclusive and it is possible that combinations could be used to further improve the performance of the algorithms \cite {Randles2}.

