\vspace{-1in}
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{NIST} Mell, Peter, and Timothy Grance. ``The NIST definition of cloud computing (draft)." \emph{NIST special publication} 800 (2011): 145.

\bibitem{Randles1}Randles, Martin, David Lamb, and A. Taleb-Bendiab. ``A comparative study into distributed load balancing algorithms for cloud computing." \emph{In Advanced Information Networking and Applications Workshops (WAINA), 2010 IEEE 24th International Conference on}, pp. 551-556. IEEE, 2010.

\bibitem{Ratan}Mishra, Ratan, and Anant Jaiswal. ``Ant colony Optimization: A Solution of Load balancing in Cloud." \emph{International Journal of Web \& Semantic Technology (IJWesT) Vol }3 (2012).

\bibitem{Randles2}Randles, Martin, Enas Odat, David Lamb, Osama Abu-Rahmeh, and A. Taleb-Bendiab. ``A Comparative Experiment in Distributed Load Balancing." \emph{In Developments in eSystems Engineering (DESE), 2009 Second International Conference on}, pp. 258-265. IEEE, 2009.

\bibitem{Madhu}Manakattu, Sheeja S., and S. D. Kumar. ``An improved biased random sampling algorithm for load balancing in cloud based systems." \emph{In Proceedings of the International Conference on Advances in Computing, Communications and Informatics}, pp. 459-462. ACM, 2012.

\bibitem{QOS} Armstrong, Django, and Karim Djemame. ``Towards Quality of Service in the Cloud." In \emph{Proc. of the 25th UK Performance Engineering Workshop.} 2009.

\bibitem{RAD} Endo, Patricia Takako, Andre Vitor de Almeida Palhares, Nadilma Nunes Pereira, Glauco Estacio Goncalves, Djamel Sadok, Judith Kelner, Bob Melander, and J. Mangs. ``Resource allocation for distributed cloud: concepts and research challenges." \emph{Network, IEEE} 25, no. 4 (2011): 42-46.

\bibitem{Berkeley} Armbrust, Michael and Fox, Armando and Griffith, Rean and Joseph, Anthony D. and Katz, Randy H. and Konwinski, Andrew and Lee, Gunho and Patterson, David A. and Rabkin, Ariel and Stoica, Ion and Zaharia, Matei. ``Above the Clouds: A Berkeley View of Cloud Computing." \emph{Technical report}, no. UCB/EECS-2009-28 (2009).

\bibitem{SRAS} Vinothina Sr, V. ``A Survey on Resource Allocation Strategies in Cloud Computing." \emph{International Journal} (2012).

\bibitem{DRMC} Goncalves, Paulo, R. O. Y. Shubhabrata, Thomas Begin, and Patrick Loiseau. ``Dynamic Resource Management in Clouds: A Probabilistic Approach." \emph{IEICE Transactions on Communications} 95, no. 8 (2012): 2522-2529.

\bibitem{Book} Han, Zhu, Dusit Niyato, Walid Saad, Tamer Başar, and Are Hjørungnes. \emph{Game theory in wireless and communication networks: theory, models, and applications.} Cambridge University Press, 2011.

\bibitem{TimeSeries} Kalekar, Prajakta S. ``Time series forecasting using Holt-Winters exponential smoothing." \emph{Kanwal Rekhi School of Information Technology} (2004).

\bibitem{Wiki1} Ski Rental problem,\ \url{http://en.wikipedia.org/wiki/Ski_rental_problem}.

\bibitem{Wiki2} Standard Deviation,\ \url{http://en.wikipedia.org/wiki/Standard_deviation}.

\bibitem{Wiki3} Forecasting Method,\ \url{http://nptel.iitm.ac.in/courses/110106045}.

\bibitem{SAS} SAS Products and Solution Documentation.

\end{thebibliography}
